Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-10 main.tex
Use plasma colormap for heatmaps.
Closes #7.
Add co authors.
I haven't removed the TODO, just waiting on Owen to confirm he's OK to
be named as an author.
Remove fingerprints.
We were not saying much about these and they were not offering much
because of the difficulty of interpretation. I think the collaboration
heatmaps are better.

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and Vincent Knight} % TODO Authors
\date{}

@@

Using a numerical method of fingerprinting based on
\cite{Ashlock2008, ashlock2009fingerprint} we can compare
strategies. The fingerprints of the top performing standard strategies are shown
in Figures~\ref{fig:comparison_fingerprint_standard}. There is a striking
similarity in the fingerprints.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/EvolvedLookerUp2_2_2.png}
        \caption{EvolvedLookerUp\_2\_2\_2}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/Evolved_HMM_5.png}
        \caption{Evolved\_HMM\_5}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16.png}
        \caption{Evolved\_FSM\_16}
    \end{subfigure}%

    \caption{Comparison of Fingerprints for Standard Tournament Top 3}
    \label{fig:comparison_fingerprint_standard}
\end{figure}

@@

Similarly to Section~\ref{sec:standard} the top performing noisy strategies
(Figure~\ref{fig:comparison_fingerprint_noisy}) have
a striking similarity in the fingerprints which indicates that the strategies
may behave similarly in principle.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/DBS.png}
        \caption{DBS}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/Evolved_ANN_5_Noise_05.png}
        \caption{Evolved\_ANN\_5\_Noise\_05}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/Evolved_FSM_16_Noise_05.png}
        \caption{Evolved\_FSM\_16\_Noise\_05}
    \end{subfigure}%

    \caption{Comparison of Fingerprints for Noisy (5\%) Tournament Top 3}
    \label{fig:comparison_fingerprint_noisy}
\end{figure}

@@

    \caption{Comparison of collaboration rates for Noisy (5\%) Tournament Top 3
    (over 10000 tournaments)}
    \label{fig:comparison_cooperation_heatmaps_noisy}
\end{figure}

@@

>>>>

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta Glynatsi} % TODO Authors
\date{}

@@

@@

@@

    \caption{Comparison of collaboration rates for the Noisy (5\%) Tournament Top 3
    (over 10000 standard tournaments)}
    \label{fig:comparison_cooperation_heatmaps_noisy}
\end{figure}

@@

% TODO Add citations to software used.
